\subsection{Architectural Scope}

%Note: To make a new line you use \\

\begin{itemize}	
		\item Platform independent
			\begin{itemize}
				\item The system should integrate and be accessible not only on 						desktop/laptop computer but also on any mobile device.
			\end{itemize}
\end{itemize}

\begin{itemize}	
		\item Distributed databases
			\begin{itemize}
				\item Each institute should maintain its own database. 
				\item In that way the database administrator would manage the data 						easily.
			\end{itemize}
\end{itemize}

\begin{itemize}	
		\item Security
			\begin{itemize}
				\item Confidentiality 
					\begin{itemize}
						\item Encrypt any sensitive data on request.  
					\end{itemize}
						
				\item Authentication 
					\begin{itemize}
						\item Hide sensitive variable data on URL (i.e. POST).
						\item Secure client-server communication.   
					\end{itemize}
				
				%William 10155865 added from Authorization to Store uploaded content
				\item Authorization 
					\begin{itemize}
						\item     
					\end{itemize}
					
				\item Non-repudiation
					\begin{itemize}
						\item On post the system should flag any suspicions of repudiation.     
					\end{itemize}					
			\end{itemize}
			
		\item Backup
		  \begin{itemize}
			  \item The system should run on multiple servers.
			  \item The system should have an automated database backup.
			  \item The system should have alternative platforms(i.e. smart phones, etc.).
		  \end{itemize}					
		  
		\item Store uploaded content (i.e. docs, images)
		  \begin{itemize}
			  \item If a user wants to upload an article or images responding to a specific post it should be possible.
		  \end{itemize}					
		
\end{itemize}
