Beal, Vangie. 'What Is Audit Trail? Webopedia'. Webopedia.com. N.p., 2015. Web. 9 Mar. 2015.\\

Codejava.net,. 'Connecting To LDAP Server Using JNDI In Java'. N.p., 2015. Web. 5 Mar. 2015.\\

Computer Security Resource Center, Computer Security Resource Center]. \url{Csrc.nist.gov. N.p.}, 2015. Web. 9 Mar. 2015.\\

Crackstation.net, (2014). Secure Salted Password Hashing - How to do it Properly. [online] Available at:\url{https://crackstation.net/hashing-security.htm} [Accessed 8 Mar. 2015].\\

Microsoft Developer Network. (n.d.). Chapter 16: Quality Attributes. Retrieved from Microsoft: \url{https://msdn.microsoft.com/en-us/library/ee658094.aspx#Scalability}\\

Mkyong.com,. 'Connect To Postgresql With JDBC Driver'. N.p., 2009. Web. 8 Mar. 2015.\\

Postgresql.org, (2015). PostgreSQL: Advantages. [online] Available at: \url{http://www.postgresql.org/about/advantages/} [Accessed 6 Mar. 2015].\\

Sei.cmu.edu, (2015). Software Architecture | Research | Previous Architecture Research | Duties, Skills, \& Knowledge of a Software Architect. [online] Available at: \url{http://www.sei.cmu.edu/architecture/research/previousresearch/duties.cfm} [Accessed 9 Mar. 2015]. \\

Solms, F. (2014, November 14). Software Architecture Design. Pretoria, Gauteng, South Africa.\\

Tutorialspoint.com,. 'JSP - Sending Email'. N.p., 2015. Web. 5 Mar. 2015.\\

Webopedia.com, (2015). What is LDAP? Webopedia. [online] Available at: \url{http://www.webopedia.com/TERM/L/LDAP.html} [Accessed 8 Mar. 2015].\\

Wikipedia. (n.d.). Maintainability. Retrieved from Wikipedia: \url{http://en.wikipedia.org/wiki/Maintainability}\\

Wikipedia. (n.d.). Scalability. Retrieved from Wikipedia: \url{http://en.wikipedia.org/wiki/Scalability#Measures}\\




